%%This is a very basic article template.
%%There is just one section and two subsections.
\documentclass{sig-alternate-05-2015}

\usepackage[]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{placeins}
%\usepackage{fullpage}
%\usepackage{amsthm}

\usepackage{amsmath,amssymb}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{algorithmic}
\usepackage{hyperref}
%to solve the hyperref problem of jumping to wrong places
\usepackage[all]{hypcap}
\usepackage{courier}
\usepackage{graphicx}
\usepackage[usenames, dvipsnames]{color}
\usepackage[framemethod=TikZ]{mdframed}
\usepackage{fancyvrb}
\usepackage{relsize}
%\graphicspath{{C:/Users/Andreas/eclipse/workspace/Synthesis_Paper/images/}}

\usepackage{float}

\renewcommand{\labelitemi}{\tiny$\blacksquare$}

\newcommand{\andreas}[1]{\textcolor{blue}{Andreas: #1}}
\newcommand{\mike}[1]{\textcolor{red}{Mike: #1}}
\newcommand{\andrew}[1]{\textcolor{green}{Andrew: #1}}

\newenvironment{requirement}
{\vspace{0.05in}
 \begin{mdframed}[roundcorner=10pt,backgroundcolor=gray!20]}
{\end{mdframed}}

\begin{document}


\title{Towards Synthesis from Assume-Guarantee Contracts involving Infinite
Theories: A Preliminary Report}

\numberofauthors{3}
\author{
\alignauthor
	Andreas Katis\\
	   \affaddr{Department of Computer Science and Engineering}\\
       \affaddr{University of Minnesota}\\
       \affaddr{200 Union Street}\\
       \affaddr{Minneapolis, MN 55455,USA}\\
       \email{katis001@umn.edu}
\alignauthor
	Andrew Gacek\\
       \affaddr{Rockwell Collins\\ Advanced Technology Center}\\
       \affaddr{400 Collins Rd. NE}\\
       \affaddr{Cedar Rapids, IA, 52498, USA}\\
       \email{andrew.gacek@\\rockwellcollins.com}
\alignauthor
	Michael W. Whalen
	   \affaddr{Department of Computer Science and Engineering}\\
       \affaddr{University of Minnesota}\\
       \affaddr{200 Union Street}\\
       \affaddr{Minneapolis, MN 55455,USA}\\
       \email{whalen@cs.umn.edu}}


\maketitle

\begin{abstract}
In previous work, we have introduced a contract-based {\em realizability checking} 
algorithm for assume-guarantee contracts involving infinite theories, such as 
linear integer/real arithmetic and uninterpreted functions over infinite domains.  
This algorithm can determine whether or not it is possible to construct a 
realization (i.e. an implementation) of an assume-guarantee contract.  
The algorithm is similar to k-induction model checking, but involves the use of 
quantifiers to determine implementability.

While our work on realizability is inherently useful for {\em virtual integration} 
in determining whether it is possible for suppliers to build software that meets 
a contract, it also provides the foundations to solving the more challenging problem 
of component synthesis. In this paper, we provide an initial synthesis 
algorithm for assume-guarantee contracts involving 
infinite theories.  To do so, we take advantage of our realizability checking 
procedure and a skolemization solver for $\forall\exists$-formulas, called
AE-VAL.  We show that it is possible to immediately
adapt our existing algorithm towards synthesis by using this solver, using a demonstration example.  We then discuss challenges towards creating a more robust synthesis algorithm.

\end{abstract}

\input{introduction}
\input{preliminaries}
\input{synthesis}
\input{related}
\input{conclusion}

\section{Acknowledgments}
This work was funded by DARPA and AFRL under contract 4504789784 (Secure Mathematically-Assured Composition of Control Models), and by NASA under contract NNA13AA21C (Compositional Verification of Flight Critical Systems), and by NSF under grant CNS-1035715 (Assuring the safety, security, and reliability of medical device cyber physical systems).
\bibliographystyle{IEEEtran}
\bibliography{document}

\end{document}
